\begin{abstract}
World foundation models (WFMs) have emerged as powerful simulators of physical environments, yet they predominantly operate in a single-view setting and lack the multi-view 3D consistency that robotic manipulation demands. Robotic systems inherently rely on multiple cameras---egocentric, eye-to-hand, and wrist-mounted---to capture complementary viewpoints for policy learning. Current multi-view world models, however, simply concatenate view tokens without explicit geometric reasoning, yielding cross-view object drift, depth inconsistency, and texture misalignment that propagate errors into downstream planning and control. We trace these failures to two fundamental deficiencies: (1)~the absence of an explicit \emph{inter-view communication mechanism}, which forces each viewpoint to generate in isolation, and (2)~the absence of a \emph{3D geometric prior}, which leaves the model without guidance on what constitutes physically correct cross-view structure. We argue that resolving both is necessary and sufficient: an information pathway across views and a geometric signal that steers it must coexist, since communication without geometric guidance collapses to trivial shortcuts, while geometric priors without an inter-view pathway cannot propagate constraints across viewpoints. Building on this analysis, we present \textbf{\methodname{}}, a framework that augments diffusion-transformer world models along two technical pillars, realized by three components. To build the \emph{inter-view communication pathway}, \textbf{Geometry-Aware Cross-View Attention} blocks open an explicit pathway across views, while \textbf{Geometric Rotary Position Embedding} encodes camera ray directions and extrinsic poses into this attention via rotary position encoding. To supply the \emph{geometric learning signal}, \textbf{Latent 3D-REPA} distills 3D-aware features from frozen 3D foundation models, ensuring the exchanged content is 3D-consistent. Built upon the DiT-based world foundation model, \methodname{} attains state-of-the-art multi-view 3D consistency on robotic manipulation benchmarks---ranking 1st on the WorldArena leaderboard and 2nd on the AgiBot-Challenge2026 leaderboard---and enables downstream applications including model-based planning, world action models, and multi-view policy post-training.
\end{abstract}
