\section{Conclusion}
\label{sec:conclusion}

We presented \methodname{}, a framework for achieving 3D-consistent multi-view generation in world foundation models for robotic manipulation. Our analysis establishes that multi-view 3D consistency requires two remedies acting at complementary levels: an architectural pathway for inter-view communication and a training-objective signal that enforces 3D-consistent content. Geometry-Aware Cross-View Attention, shaped by Geometric Rotary Position Embedding, opens the pathway through which viewpoints exchange information along geometrically corresponding tokens; Latent 3D-REPA supplies the geometric learning signal that makes the exchanged content faithful to true 3D structure. We showed that neither remedy alone suffices---a pathway without geometric supervision degenerates into trivial shortcuts, while a geometric prior without an inter-view pathway cannot propagate constraints across views---and that their combination, addressing both the architectural and objective levels at once, yields consistent multi-view 3D generation.

Built upon the DiT-based world foundation model, \methodname{} attains state-of-the-art multi-view 3D consistency on robotic manipulation benchmarks, leading on reconstruction-based, geometric, and scene-consistency metrics across both text- and action-conditioned settings. This improved consistency carries over to downstream embodied tasks: model-based planning benefits from physically plausible imagined trajectories, world action models exhibit stronger action-visual causal alignment, and multi-view policy post-training yields more effective manipulation policies.

Several promising directions remain for future work. First, incorporating \emph{physical interaction modeling}, such as contact dynamics, deformable objects, and fluid simulation, would push 3D consistency beyond geometry into physics-aware world modeling. Second, scaling to \emph{long-horizon planning} scenarios will require maintaining 3D consistency over extended temporal rollouts, potentially through hierarchical or recurrent architectures. Third, by coupling our world model with a World Action Model (WAM), we aim to build a \emph{world-model-driven data closed loop} for embodied intelligence: the world model generates diverse imagined experiences, the WAM learns from these experiences to improve its policy, and the improved policy in turn collects higher-quality real-world data to further refine the world model---enabling continuous self-improvement and autonomous evolution of embodied agents. Fourth, we plan to develop \emph{industrial manufacturing foundation models} built upon our world modeling framework, targeting applications such as dynamic scheduling of production lines and real-time control of manufacturing processes, where accurate physical simulation and multi-view monitoring are critical for intelligent manufacturing.
